---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit the README.Rmd file -->


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = TRUE)

library(ggplot2)
library(dplyr)
```

# Final Project - Team XXX

This repository serves as a starter repo for your final project, and this Rmd is supposed to serve as a starter file for your project report.

## Repo Structure

The structure sketched out below is an idea of what your repository might look like. You can use it as a starting base and change according to your needs. But think about the changes that you make!


    -- code
    |   |   -- any R scripts you need but don't want to include directly in the write-up
    -- data
    |   |   -- csv files (cleaned data)
    -- data-raw
    |   |   -- raw data files 
    |   |   -- data description files, origin
    |   |   -- Codebook
    -- final-project.Rmd
    -- images  # only images that are not created by the Rmd
    -- LICENSE
    -- README.md
    -- README.Rmd
    -- README_files # folder with files created during the knitting process



# Project report


## Title of your project

Authors: First Name Last Name, First Name Last Name, ...

### Abstract (TL;DR)

An abstract is a quick summary of your work. Ideally it should motivate someone to read the rest of the paper. Include one sentence each on

- what is the project about?
- what is the motivation for doing it?
- what data is your work based on? and where does it come from?
= what are your main findings? (one sentence each)

### Intro/Background/Motivation

What is the topic of your project, why is it relevant?

At the end of the Intro, write a sentence describing what each of the (result) sections is about, e.g. in section 3 we show the relationship between XXX and YYY, section 4 also considers the effect of variable ZZZ. ...   

Somewhere at the beginning of your project, include a code chunk that includes all of the R packages you are using throughout. In this document, the setup code chunk is called `setup` (see line 8)
Also make sure to set defaults for the code chunks - like should they be visible? (probably not: echo=FALSE). Do you want to automatically include warnings? (probably yes, for creating the Rmd, to make sure that all warnings are accounted for)

### Quick Data Summary

What are the variables that you will be using in the main part of the report? What are their ranges? 
You could include a table with variable names, a short explanation, and (very broad) summary statistics.

### Results

Each line of exploration is supposed to be featured in one of the Results sections. Make sure to change to more interesting section headers!

#### Results 1

In your write-up, make sure to refer to the figure. 
You can include a hyperlink to @code-chunk-name using the name of the code chunk (make sure, to give each code chunk a different name) by placing an `@` in front of its name.

```{r code-chunk-name, echo=FALSE, fig.cap="This is the figure caption. Make sure to use the description we practised in the homework: first sentence describes structure of the plot, second sentence describes main finding, third sentence describes outliers/follow-up.", message = FALSE}

mtcars %>% 
  ggplot(aes(x = wt, y = mpg)) + 
  geom_point()
```


#### Results 2

#### Results 3

...

### Data source

Where does the data come from, who owns the data?
Where are all the scripts that you need to clean the data?
